Bootstrap learning via modular concept discovery

### 2013-04-22 drafts/ijcai2013/ijcai13.tex
Removed unneccessary vspaces.

\setcounter{subfigure}{0} 
\begin{figure}[ht]
\centering
\includegraphics[width=1.0\linewidth]{figures/symreg3frontiers.pdf}
\vspace{-.2cm}
\caption{Learning curves as a function of frontier size.  As frontier
  size is increased, curves plateau closer to $100\%$ performance. A
  baseline search over $150000$ expressions only hits $3\%$ of the
  tasks (dashed pink line). \label{fig:symregLearning}}
\vspace{-.3cm}
\end{figure}
\begin{figure}[ht]
\includegraphics[width=1.07\linewidth]{figures/symRegDiffCurricula.pdf}
\caption{How do different task sets affect learning curves? Learning
  curves at frontier size of $10000$ for different task
  sets.} 
\label{fig:symregCurricula}

@@

\end{subfigure}
\vspace{-.3cm}
\caption{Learning curves from Boolean function learning
  experiments. (a) Learning curves for various frontier sizes on task
  set of circuit based Boolean functions. (b) 10
  learning curves for frontier size of 2000 on a task set consisting
  of all Boolean functions of cardinality 3 or smaller. Note how most
  of the trajectories get stuck in a local minimum around
  $50\%$.\label{fig:boolLearningCurves}

}
\vspace{-.5cm}
\end{figure}

\section{Conclusion}
This work brings together ideas from various areas of research --
hierarchical Bayes, learning to learn, minimum description length
learning, and learning programs -- to provide a proof of concept for
how bootstrap learning of abstract composable concepts can rapidly
improve search performance.  We show that this approach can learn
successfully even in domains for which the solution space is not
smooth and the error signal is all or none, where the only sense of
locality to guide learning is the modular and compositional structure
of the solutions that the algorithm itself builds.

>>>>

\setcounter{subfigure}{0} 
\begin{figure}[ht]
\centering
\includegraphics[width=1.0\linewidth]{figures/symreg3frontiers.pdf}
%\vspace{-.2cm}
\caption{Learning curves as a function of frontier size.  As frontier
  size is increased, curves plateau closer to $100\%$ performance. A
  baseline search over $150000$ expressions only hits $3\%$ of the
  tasks (dashed pink line). \label{fig:symregLearning}}
%\vspace{-.3cm}
\end{figure}
\begin{figure}[ht]
\includegraphics[width=1.07\linewidth]{figures/symRegDiffCurricula.pdf}
\caption{How do different task sets affect learning curves? Learning
  curves at frontier size of $10000$ for different task
  sets.} 
\label{fig:symregCurricula}

@@

\end{subfigure}
%\vspace{-.3cm}
\caption{Learning curves from Boolean function learning
  experiments. (a) Learning curves for various frontier sizes on task
  set of circuit based Boolean functions. (b) 10
  learning curves for frontier size of 2000 on a task set consisting
  of all Boolean functions of cardinality 3 or smaller. Note how most
  of the trajectories get stuck in a local minimum around
  $50\%$.\label{fig:boolLearningCurves}

}
%\vspace{-.5cm}
\end{figure}

\section{Conclusion}
This work brings together ideas from various areas of research --
hierarchical Bayes, learning to learn, minimum description length
learning, and learning programs -- to provide a proof of concept for
how bootstrap learning of abstract composable concepts can rapidly
facilitate problem solving in the absence of domain specific
knowledge. We show that this approach can learn successfully even in
domains for which the solution space is not smooth and the error
signal is all or none, where the only sense of locality to guide
learning is the modular and compositional structure of the solutions
that the algorithm itself builds.
